### 2025-05-07 paper/paper.tex
Update paper.tex

Each intersection is managed by an instance of {\tt DQNAgent} (in policies.py), which maintains both an \emph{online} network and a \emph{target} network. At initialization, we load the target’s weights from the online network and set up an Adam optimizer (learning rate 0.001), a discount factor $\gamma=0.99$, and an $\varepsilon$‐greedy exploration schedule that decays $\varepsilon$ from 1.0 to 0.05 by a factor of 0.995 per learning step. Experiences are stored in a fixed‐capacity deque buffer (size 5,000), and we sample mini‐batches of 32 transitions once the buffer is sufficiently large. In each learn() call we compute the predicted Q‐values for state–action pairs, form TD‐targets via 
\[
Q_{\mathrm{target}} \;=\; r \;+\; \gamma\,(1 - d)\,\max_{a'} Q_{\mathrm{target}}(s', a')
\]
and minimize the mean‐squared error between predictions and targets. After each gradient update, we decay $\varepsilon$, and every 100 updates we synchronize the target network with the online network. To scale this to multiple intersections, we wrap several {\tt DQNAgent} objects in {\tt MultiDQNAgent}, forwarding action selection, memory storage, and learning calls independently to each agent.

>>>>

Each intersection is managed by an instance of {\tt DQNAgent} (in policies.py), which maintains both an \emph{online} network and a \emph{target} network. At initialization, we load the target’s weights from the online network and set up an Adam optimizer (learning rate 0.001), a discount factor $\gamma=0.99$, and an $\varepsilon$‐greedy exploration schedule that decays $\varepsilon$ from 1.0 to 0.05 by a factor of 0.995 per learning step. Experiences are stored in a fixed‐capacity deque buffer (size 5,000), and we sample mini‐batches of 32 transitions once the buffer is sufficiently large. In each learn() call we compute the predicted Q‐values for state–action pairs, form TD‐targets via 
\[
Q_{\mathrm{target}} \;=\; r \;+\; \gamma\,(1 - d)\,\max_{a'} Q_{\mathrm{target}}(s', a')
\]
and minimize the mean‐squared error between predictions and targets. This target arises directly from the Bellman optimality equation and serves as the reference value toward which our online Q‐network is trained. Below is a concise, technical explanation of each component. The scalar \textit{r} represents the instantaneous reward signal returned by the environment upon executing action \textit{a} in state \textit{s}. In traffic‐signal control, we typically define \textit{r} as a negative congestion metric (e.g., the sum of queue lengths), so that higher rewards correspond to smoother traffic flow. This term anchors the TD target in the actual, observed outcome of the agent’s decision. $\gamma \in [0,1)$ is the temporal‐discount coefficient that geometrically attenuates the contribution of future returns.  
A value of $\gamma = 0.99$ indicates that the agent values rewards received one step later at $99\%$ of their original magnitude.  
By tuning $\gamma$, one controls the trade‐off between short‐term gains and long‐horizon optimization. Lower $\gamma$ leads to myopic behavior, while values approaching 1 emphasize long‐term planning. The binary flag $d$ equals $1$ if the sampled transition terminates an episode (i.e., $s'$ is terminal), and $0$ otherwise.  
Multiplying by $(1 - d)$ ensures that, in terminal states, no bootstrapped future value is added, thus strictly enforcing that $Q_{\mathrm{target}} = r$ when the episode ends. This prevents spurious propagation of post‐terminal $Q$-values. The operator $\max_{a'} Q(s',a')$ extracts the highest $Q$‐value estimate across all possible actions $a'$ in the successor state $s'$, as evaluated by the target network. This “greedy” selection embodies the assumption that, after the current transition, the agent will henceforth behave optimally, consistently choosing the action with maximal expected return. By summing the immediate reward $r$ and the discounted maximal next‐state value (when $d = 0$), we obtain a single‐step bootstrap estimate of the true return. During training, the online network’s prediction $Q_{\mathrm{pred}}(s,a)$ is regressed toward $Q_{\mathrm{target}}$ via mean‐squared error. Periodic synchronization of the target network stabilizes training by holding the bootstrap reference fixed for a configurable number of gradient updates. After each gradient update, we decay $\varepsilon$, and every 100 updates we synchronize the target network with the online network. To scale this to multiple intersections, we wrap several {\tt DQNAgent} objects in {\tt MultiDQNAgent}, forwarding action selection, memory storage, and learning calls independently to each agent.
